---
title: "gya-survey-report"
author: "James Robinson; Kristina Tietjen"
date: "18 July 2016"
output: html_document
---

```{r, echo=FALSE}
## load in survey data
setwd()
survey<-read.csv("data/")

## load required packages
require(gridExtra); require(tidyr)
```

### GYA surveys: summary statistics

As of `r date()`, `r, dim(surveys)[1]` from `r, length(unique(surveys$Country_work))` countries have been completed.

The majority of surveys were completed by researchers based in Canada (n = `r, length(surveys[surveys$Country_work=="Canada",])[1]`), followed by USA (n = `r, length(surveys[surveys$Country_work=="USA",])[1]`) and the UK (n = `r, length(surveys[surveys$Country_work=="UK",])[1]`).

```{r, echo=FALSE, fig.cap="Survey responses by country"}
ggplot........
```

```{r, echo=FALSE, fig.cap="Survey responses by field of research (global and Canada)"}
g1<-ggplot........

g2<-ggplot........

grid.arrange(g1, g2)
```

### GYA surveys: Canada

#### Part 1 - Type of Research Conducted
```{r, echo=FALSE, fig.cap="Current vs. past research type (Canada)"}
## make sure that Use-inspired is the middle level in the legend
g1<-ggplot()


g2<-ggplot()

grid.arrange(g1, g2)
```

```{r, echo=FALSE, fig.cap="Reason for change in research over past 10 years (Canada)"}
## order bars from highest to lowest

# Change in the past 10 years? (yes, no, can't comment)
g1<-ggplot()

# What is your main reason for change?
g2<-ggplot()

grid.arrange(g1, g2, nrow=1)
```


#### Part 4 - Funding Trends

```{r, echo=FALSE, fig.cap="Perceived importance of fundamental research to Canada"}
## order bars from very important (left) to can't comment (right)
ggplot()

```


```{r, echo=FALSE, fig.cap="Perceived change in research priority by Canadian government"}
## order bars into applied > use > fundamental > no change
ggplot()

```


```{r, echo=FALSE, fig.cap="Anticipated change in research funding in next 5 years "}
## change in funding on the x-axis, and colours = type of research
## order bars into increase considerably (left) to decrease considerably (right), then no comment at the far right
ggplot()

```


```{r, echo=FALSE, fig.cap="Effect of change in research funding on research careers of next generation"}

## order bars into increase considerably (left) to decrease considerably (right), then no comment at the far right
ggplot()

```



ADD GENDER TO PLOTS.....