---
title: "Canadian online survey on fundamental research"
author: ''
date: "16 September 2016"
output:
  pdf_document: null
  fig_width: 18
  html_document: default
  fig_height: 4
---

**Introduction**
In addition to the official data presented in Chapters 2 and 3, we also developed and ran a quantitative online survey to query researchers about their perceptions of, and experiences with, funding for fundamental research. An important aim of the survey was to provide an understanding researcher's personal experiences and outlook on the research funding landscape in Canada. We had an excellent response to the survey, with over 1300 Canadian researchers completing it, suggesting that fundamental research funding is a high priority topic for Canadian researchers. Herein, we detail the survey questions and results. 

**Methods**  
Online Survey  
The survey was open to researchers from all disciplines (e.g. science, social sciences, humanities, engineering, medicine) and career stages, with the proviso that they had some experience applying for research funding. The survey gathered detailed information in four major areas: 1) the types of research the scholars conduct (fundamental, use-inspired, applied), 2) the extent of external partnerships in their research, 3) their grant success rates, and 4) how important they perceive fundamental research is to the Canadian federal government and its future prospects in Canada. The survey also enquired how each of these factors have changed over time for the researchers. Finally, the survey gathered basic information from each respondent about gender, discipline, career stage and the year their PhD was obtained. The full survey is provided in Appendix 2. 

The online survey was open from the end of May through early October 2016, and ran on the Fluid Surveys platform (fluidsurveys.com). Note that the survey was open to researchers from any country in the world because it is was run as part of a global survey through the Global Young Academy. To disseminate the survey to Canadian researchers, we gathered email addresses from Canadian university websites for as many faculty members as possible and emailed individual researchers directly. We also shared the survey broadly on social media, as well as through the Global Young Academy network, on scientific list serves, and through personal connections. 

Survey Data Analysis  
To extract survey responses for Canadian researchers, we selected all respondents who reported 'Canada' as their country of work, as well as those respondents who did not report a country of work (i.e. field was blank) but whose location was within Canada. We conducted all statistical analyses in the open source software R (Version 3.3.1).
**Note that numbers not all the same because respondents did not always answer every question**

<!-- Import Canadian data, calculate sample sizes -->
```{r, echo=FALSE, message=FALSE, hide=TRUE, warning=FALSE, message=FALSE} 
## CHANGE WORKING DIRECTORY FOR YOUR LOCAL MACHINE BEFORE KNITTING ##
setwd("/Users/kristinatietjen/Documents/git_hub/gya-research/writing")
#setwd("/Users/IMAC3/Documents/git-jpwrobinson/gya-research")
#setwd("/Users/jpwrobinson/Documents/git_repos/gya-research")
#setwd("/Users/Julia_2013MacBookAir/Desktop/GitRepos/gya-research/writing")
## load in survey data
survey<-read.csv(file="../data/gya-without-incomplete.csv")
n.Cdn.res <- survey[survey$Country_work=="Canada" | (!(survey$Country_work=="Canada") & 
             survey$Country_work=="" & survey$Country=="Canada"),]  #Count how many responses from Canadian researchers
survey.what<-read.csv(file="../data/gya-country-responses.csv")
research<-read.csv(file="../data/gya-surveys-cleaned-research.csv")
#research.past<-read.csv(file="data/gya-surveys-cleaned-research-past.csv")
research.change<-read.csv(file="../data/gya-change-reason.csv")
part4<-read.csv(file="../data/gya-survey-part4.csv")
part2.b.a<-read.csv(file="../data/gya-part2.before.after.csv")
part2.change<-read.csv(file="../data/gya-part2.change.csv")
part2.reason<-read.csv(file="../data/gya-part2.reason.csv")
part2.view<-read.csv(file="../data/gya-part2.view.csv")
part1.view<-read.csv(file="../data/gya-part1.view.csv")
part3.change<-read.csv(file="../data/gya-part3.change.csv")
part3.grants.long<-read.csv(file="../data/gya-part3.grants.long.csv")
part3.success.long<-read.csv(file="../data/gya-part3.success.long.csv")
part3.prac.long<-read.csv(file="../data/gya-part3.prac.long.csv")
part3.part.long<-read.csv(file="../data/gya-part3.part.long.csv")
p3_master.long<-read.csv(file="../data/gya-p3_master.long.csv")
p3_master <- read.csv(file="../data/gya-p3_master.csv")

#Gender:
n.Cdn.res.men <- n.Cdn.res[n.Cdn.res$gender=="Male",]               #Count how many responses from Canadian male researchers
percent.men<-((dim(n.Cdn.res.men)[1])/(dim(n.Cdn.res)[1]))*100      #Calculate the % of responses from Canadian male researchers
n.Cdn.res.women <- n.Cdn.res[n.Cdn.res$gender=="Female",]           #Count how many responses from Canadian female researchers
percent.women<-((dim(n.Cdn.res.women)[1])/(dim(n.Cdn.res)[1]))*100  #Calculate the % of responses from Canadian female researchers

#Career Stage Tabulations:
#table(n.Cdn.res$what_participant_group)
n.Cdn.seniorac <- n.Cdn.res[n.Cdn.res$what_participant_group=="Senior academic researcher with >10 years of experience applying for research grants",]
percent.seniorac<-((dim(n.Cdn.seniorac)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from Canadian senior academic researchers
n.Cdn.earlyac <- n.Cdn.res[n.Cdn.res$what_participant_group=="Early career academic researcher with <10 years experience applying for research grants since completion of PhD",]
percent.earlyac<-((dim(n.Cdn.earlyac)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from Canadian early academic researchers
n.Cdn.pdf <- n.Cdn.res[n.Cdn.res$what_participant_group=="Postdoctoral fellow or research assistant with experience applying for research grants, or anticipating the need to apply for grants in the near future",]
percent.pdf<-((dim(n.Cdn.pdf)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from Canadian post-docs
n.Cdn.nonACearly <- n.Cdn.res[n.Cdn.res$what_participant_group=="Non-academic researcher conducting or managing research in industry or government with <10 years of experience",]
percent.nonACearly<-((dim(n.Cdn.nonACearly)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from early career non-academics
n.Cdn.nonACsenior <- n.Cdn.res[n.Cdn.res$what_participant_group=="Non-academic researcher conducting or managing research in industry or government with >10 years of experience",]
percent.nonACsenior<-((dim(n.Cdn.nonACsenior)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from early career non-academics
n.Cdn.unk <- n.Cdn.res[n.Cdn.res$what_participant_group=="",]
percent.unk<-((dim(n.Cdn.unk)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from unknown career stage

#Discipline Tabulations:
n.natural <- n.Cdn.res[n.Cdn.res$field_research=="Natural Science",]
percent.natural <- ((dim(n.natural)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from Canadian natural scientists
n.physics <- n.Cdn.res[n.Cdn.res$field_research=="Physical Science (eg. math, physics, chemistry, computer science)",]
percent.physics <- ((dim(n.physics)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from Canadian physical scientists
n.med <- n.Cdn.res[n.Cdn.res$field_research=="Medicine and Life Science",]
percent.med <- ((dim(n.med)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from Canadian med/life scientists
n.eng <- n.Cdn.res[n.Cdn.res$field_research=="Engineering",]
percent.eng <- ((dim(n.eng)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from Canadian engineering scientists
n.int <- n.Cdn.res[n.Cdn.res$field_research=="Interdisciplinary Science",]
percent.int <- ((dim(n.int)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from Canadian interdisciplinary scientists
n.ssh <- n.Cdn.res[n.Cdn.res$field_research=="Social Science / Humanities",]
percent.ssh <- ((dim(n.ssh)[1])/(dim(n.Cdn.res)[1]))*100 #Calculate the % of responses from Canadian interdisciplinary scientists

```

**Results**  
In total, `r dim(n.Cdn.res)[1]` Canadian researchers completed the online survey. Of these, almost three quarters were male (`r ceiling(percent.men)`%) and one quarter were female (`r round(percent.women)`%); a very small proportion either did not input their gender or selected other. Almost all of the survey respondents (`r round(sum(percent.seniorac,percent.earlyac))`%) were either senior academics (`r round(percent.seniorac)`%), defined as those researchers with more than ten years experience applying for research grants since completion of their PhD, or early career academics (`r round(percent.earlyac)`%) (Figure 4.1). A small proportion of responses also came from post-doctoral researchers (`r round(percent.pdf)`%), non-academic researchers (`r  round(sum(percent.nonACearly,percent.nonACsenior))`%), or those who did not indicate their career stage (`r round(percent.unk, digits=1)`%).

Researchers from many different disciplines were represented in the survey. Almost sixty per cent of responses came from either the natural or physical sciences (Figure 4.2). The remaining responses were spread amongst the medical and life sciences (`r round(percent.med)`%), engineering (`r round(percent.eng)`%), interdisciplinary research (`r round(percent.int)`%), and social sciences and humanities (`r round(percent.ssh)`%). 

<!-- Generate Canadian career stage figure -->
```{r, echo=FALSE, message=FALSE, fig.cap="Figure 4.1 Number of Canadian survey respondents by career stage", warning=FALSE, fig.width=14}
## load required packages
require(gridExtra); require(tidyr); require(ggplot2); require(stringr);require(RColorBrewer); require(colorRamps); require(plotrix); require(plyr)

theme_set(theme_bw())
## setting colour scale to keep colours identical between similar plots
## myColors <- brewer.pal(6,"Set1")
can.field<-survey.what[survey.what$Country_work=="Canada" | (!(survey.what$Country_work=="Canada") & survey.what$Country_work=="" & survey.what$Country=="Canada"),]

experience_can<-data.frame(table(can.field$what_participant_group))
experience_can<-experience_can[!experience_can$Var1=="",]
experience_can<-droplevels(experience_can)

experience_can$Var1<-revalue(experience_can$Var1, c("Early career academic researcher with <10 years experience applying for research grants since completion of PhD" = "Early career academic researcher", "Non-academic researcher conducting or managing research in industry or government with >10 years of experience" = "Non-academic research > 10 yrs experience", "Non-academic researcher conducting or managing research in industry or government with <10 years of experience" = "Non-academic researcher < 10 yrs experience", "Postdoctoral fellow or research assistant with experience applying for research grants, or anticipating the need to apply for grants in the near future" = "Postdoc or RA", "Senior academic researcher with >10 years of experience applying for research grants" = "Senior academic researcher"))
experience_can$Var1<-reorder(experience_can$Var1, experience_can$Freq)

# assign colour scale
myColors<-(brewer.pal(9, "Blues"))
myColors<-myColors[-c(1:2)]
names(myColors)<- levels(experience_can$Var1)
colScale <- scale_fill_manual(name = "Var1",values = myColors)

ggplot(experience_can, aes(x = reorder(Var1, -Freq), Freq, fill=Var1)) + 
  geom_bar(stat='identity',position = position_dodge(width=0.5)) + 
  geom_text(aes(label=Freq, vjust=-1))+
  scale_x_discrete(labels=c("Senior academic", "Early career academic", "Postdoc or RA", "Senior non-academic", "Early career non-academic")) +
  labs(y="No. of responses", x="Career stage") +
  guides(fill=guide_legend(title=NULL, reverse=TRUE, nrow=3)) +  
  theme(legend.title=element_blank(), 
        legend.text=element_text(size=10), 
        axis.text=element_text(size=14),
        axis.text.x=element_text(angle=0, size=12), 
        axis.title=element_text(size=15),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) + 
  colScale+ ylim(c(0, 900)) + guides(fill=FALSE)
```

<!-- Generate Canadian research discipline figure -->
```{r, echo=FALSE, fig.cap="Figure 4.2 Survey responses by field of research", warning=FALSE, fig.width=14}
field.can<-with(survey.what[survey.what$Country_work=="Canada" | (!(survey.what$Country_work=="Canada") & survey.what$Country_work=="" & survey.what$Country=="Canada"),], data.frame(table(field_research)))
field.can<-field.can[!field.can$field_research=="",]
field.can$field_research<-reorder(field.can$field_research, field.can$Freq)
field.can$field_research<-revalue(field.can$field_research, c("Physical Science (eg. math, physics, chemistry, computer science)" = "Physical Science"))

## setting colour scale to keep colours identical between similar plots
myColors<-(brewer.pal(9, "Blues"))
myColors<-myColors[-c(1)]
names(myColors) <- levels(field.can$field_research)
colScale <- scale_fill_manual(name = "field_research",values = myColors)

ggplot(field.can, aes(x = reorder(field_research, -Freq), Freq, fill=field_research)) + 
    geom_bar(stat='identity',position = position_dodge(width=0.5)) + 
  ylim(c(0, 400)) +
  labs(y="No. of responses",x="", title="")  +
  scale_x_discrete(labels=c("Natural\n Science", "Physical\n Science", "Medicine &\n Life Science", "Engineering", "Interdisciplinary\n Science", "Social Science/\n Humanities", "Other")) +
  geom_text(aes(label=Freq), vjust=-0.25) + 
  theme( axis.text=element_text(size=14),
         axis.text.x=element_text(angle=0, size=14),
         axis.title=element_text(size=14),
         panel.grid.major = element_blank(),
         panel.grid.minor = element_blank()) + 
  guides(fill=FALSE) + colScale
```

------ Rmd FILE IS FIXED DOWN TO HERE
*4.1 Type of Research Conducted* 
Canadian survey respondents included researchers conducting all three types of research: fundamental, use-inspired, and applied. Very few researchers considered themselves to only do one type of research: insert %s of who think they do all of f, u, or a. X% of researchers consider that over half of their research program is in fundamental science......

SOMEHOW HAVE TO MAKE SENSE OF THE RESPONSES AND PLOT FOR THE % OF RESEARCH IN THE THREE CATEGORIES. Almost one third of researchers reported that the types of research they conduct has shifted over the past ten years (Figure 3). By far, the most reported reason for this change was funding (Figure 4). This suggests.....  However, opinions about these changes were varible, with one quarter of respondents viewing them as slightly negative, one quarter slightly positive and one quarter very positive (Figure X).

<!-- Generate figure showing current and past fundamental, use-inspiried, and applied research %s -->
```{r, echo=FALSE, fig.cap="Figure 4.3 Funding allocation to fundamental, use-inspired and applied research categories. Reseachers were questioned about the percentage of funding allocated to Fundamental, Use-inspired or Applied research in the past and in their current research.", message=FALSE, warning=FALSE, fig.width=10}

## make sure that Use-inspired is the middle level in the legend
res.plot<-subset(research, type%in%c("percent_fundemental_research_current",  "percent_Applied_Research_current" , "percent_Use_inspired_Research_current","percent_Applied_Research_past",  "percent_Fundamental_Research_past" , "percent_Use_inspired_Research_past"))

res.plot$percent<-str_replace_all(res.plot$percent, "%", "")
res.plot$percent<-as.numeric(as.character(res.plot$percent))
res.plot$type<-as.character(res.plot$type)

# add time variable
res.plot$time<-ifelse(grepl( "current", res.plot$type),"Current", "Past")
res.plot$type[res.plot$type=="percent_Applied_Research_past"]<-"Applied"
res.plot$type[res.plot$type=="percent_Applied_Research_current"]<-"Applied"
res.plot$type[res.plot$type=="percent_Fundamental_Research_past"]<-"Fundamental"
res.plot$type[res.plot$type=="percent_fundemental_research_current"]<-"Fundamental"
res.plot$type[res.plot$type=="percent_Use_inspired_Research_past"]<-"Use-inspired"
res.plot$type[res.plot$type=="percent_Use_inspired_Research_current"]<-"Use-inspired"

# change order of the levels
res.plot$time<-as.factor(res.plot$time)
res.plot$time<-factor(res.plot$time, levels(res.plot$time)[c(2,1)])

res.plot$type<-as.factor(res.plot$type)
res.plot$type<-factor(res.plot$type, levels(res.plot$type)[c(2,3,1)])

res.plot$time<-factor(res.plot$time)
res.plot$time<-factor(res.plot$time, levels(res.plot$time)[c(1,2)])

myColors<-(brewer.pal(9, "Blues"))
myColors<-myColors[c(5,9)]
colScale <- scale_fill_manual(name = "time",values = myColors)

res.plot<-res.plot[res.plot$Country_work=="Canada" | (!(res.plot$Country_work=="Canada") & res.plot$Country_work=="" & res.plot$Country=="Canada"),]

ggplot(res.plot, aes(percent, fill=time)) +
    geom_histogram(position='dodge', binwidth=10, bins=seq(0, 100, 10))  +
    guides(fill=guide_legend(title=NULL, reverse=FALSE, nrow=2)) +
    labs(x="% funding", y="No. responses", title="")+
    theme(panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          strip.text.y = element_text(size=12, face="bold", color="black"),
          strip.background = element_rect(colour="white", fill="white"),
          legend.position=c(0.8, 0.2)) + 
    facet_wrap(~type, nrow=3) + colScale +
  scale_x_continuous(breaks=seq(0,100,10))

```

#### Part 2 - External Partnerships
```{r, echo=FALSE, fig.cap="Figure 4.6 Current vs past level of partnership outside of academia. Researchers indicated the level of partnership that their current and past (10 years ago) research program had outside of academia).", warning=FALSE}
part2.b.a<-part2.b.a[part2.b.a$Country_work=="Canada" | (!(part2.b.a$Country_work=="Canada") & part2.b.a$Country_work=="" & part2.b.a$Country=="Canada"),]

b.part<-data.frame(table(part2.b.a$partnership_outside_before))
b.part$time<-"Past"
a.part<-data.frame(table(part2.b.a$partnership_outside))
a.part$time<-"Current"

part<-rbind(a.part, b.part)
part$Var1<-factor(part$Var1, levels(part$Var1)[c(1,4,3,2)])
part$time<-factor(part$time)
part$time<-factor(part$time, levels(part$time)[c(2,1)])

myColors<-(brewer.pal(9, "Blues"))
myColors<-rev(myColors[c(9, 6)])
colScale <- scale_fill_manual(name = "Var1",values = myColors)

ggplot(part, aes(x=Var1, y=Freq, fill = time),  ylim(0,375)) + 
  geom_bar( stat='identity', position="dodge") +
  geom_text(aes(label=Freq), position=position_dodge(width=1), vjust=-0.8) +
  labs(x="", y="No. of Responses", fill="")+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle=0), 
        legend.position=c(0.2, 0.9), 
        legend.title=element_blank()) +
  colScale
```

```{r, echo=FALSE, fig.cap="Figure 4.7 Reasons for change in level of external research partnerships over the past decade.", warning=FALSE}
### was there change
#canada<-subset(part2.change, Country=="Canada")
#canada<-part2.change[part2.change$Country_work=="Canada" | (!(part2.change$Country_work=="Canada") & part2.change$Country_work=="" & part2.change$Country=="Canada"),]
#change.part.ca<-data.frame(table(canada$partnership_change_10yrs))
#change.part.ca$Var1<-revalue(change.part.ca$Var1, c("Can't comment (new researcher)"="Can't comment"))
#change.part.ca$Var1<-factor(change.part.ca$Var1, levels=c("Yes", "No", "Can't comment"))
#myColors<-(brewer.pal(9, "Blues"))
#myColors<-myColors[c(9, 7,5)]
#g1<-ggplot(data=change.part.ca, aes(x=Var1, y=Freq, fill=Var1))+ 
#    geom_bar(stat='identity') + 
#    guides(fill=FALSE) + 
#    labs(x="", y="No. of responses",title="")+
#  geom_text(aes(label=Freq), vjust=-0.5)+
#  theme(panel.grid.major = element_blank(),
#        panel.grid.minor = element_blank()) + 
#  scale_fill_manual(name = "Var1",values = myColors) +
#  annotate('text', 3.25,606, label="(a)", size=7)

### reason
part2.reason<-part2.reason[part2.reason$Country_work=="Canada" | (!(part2.reason$Country_work=="Canada") & part2.reason$Country_work=="" & part2.reason$Country=="Canada"),]
reason.pt.long<-gather(part2.reason, change.reason, yes, -Country,-Country_work, -gender, -Location, -what_participant_group, -field_research)
sum.canada<-data.frame(table(reason.pt.long$change.reason, reason.pt.long$yes))

sum.canada$Var1<-revalue(sum.canada$Var1, c("reason_partnership_change_career" = "Career", "reason_partnership_change_funding" = "Funding", "reason_partnership_change_interest" = "Interest", "reason_partnership_change_other" = "Other", "reason_partnership_change_socially"  = "Social"))
sum.canada$Var1<-reorder(sum.canada$Var1, -sum.canada$Freq)

myColors<-(brewer.pal(9, "Blues"))
myColors<-myColors[c(9, 8,7,6,5,3)]

g2<-ggplot(sum.canada, aes(x=Var1, y=Freq, fill=Var1)) + 
    geom_bar(stat='identity')+  guides(fill=FALSE) +
    theme(axis.text.x = element_text(angle=0, vjust=0.5),
          legend.position=c(0.8, 0.8), 
          legend.title=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) + 
  geom_text(aes(label=Freq), vjust=-0.5)+
   ylim(c(0, 420))+
  labs(x="", y="", title="")+scale_fill_manual(name = "Var1",values = myColors)
print(g2)
#annotate('text', 5,420, label="(b)", size=7)+  
#grid.arrange(g1, g2, nrow=1)
```

```{r, echo=FALSE, fig.cap="Figure 4.8 View of change in external partnerships. Researchers were asked how they viewed the change in the level of partnership with external groups.", warning=FALSE}
#canada<-subset(part2.view, Country=="Canada")
canada<-part2.view[part2.view$Country_work=="Canada" | (!(part2.view$Country_work=="Canada") & part2.view$Country_work=="" & part2.view$Country=="Canada"),]
view<-data.frame(table(canada$view_change_partnership))
# change order of the levels

view$Var1<-factor(view$Var1, levels(view$Var1)[c(5,3,1,2,4)])


ggplot(view, aes(x=Var1, y=Freq, fill=myColors[1])) + geom_bar(stat='identity')+
  geom_text(aes(label=Freq, vjust=-0.5))+
  guides(fill=FALSE)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle=0, vjust=0)) + 
  labs(x="", y="No. of Responses") + colScale

```

*4.2 External Partnerships*   
The extent to which research is conducted with partners outside of academia, including in industry and non-governmental sectors, may also be considered as an indicator of use-inspired or applied research. Almost all respondents (88%) reported that their current research includes external partners to some degree: fifty-nine per cent reported some partnerships and a further quarter (27%) reported strong partnerships (Figure 4.6). Less than 1% reported conducting their research exclusively with partners outside of academia. 

Over the past decade, there has been a sharp decline in the number of researchers with no external partnerships: only 12% of respondents reported having no partnerhips in their current research program, whereas almost half of respondents (44%) reported having no partnerships in the past (Figure 4.6). The number of strong external partnerships also has increased over time from 11% to 27% (Figure 4.6). 

Funding was the driving force behind the shift towards external partnerhips. Half of Canadian respondents reported that they developed external partnerships in order to secure funding (Figure 4.7). The remaining half of respondents developed partnerships out of interest (24%), or for career (12%) or social reasons (<1%) (Figure 4.7).

Perspectives on these changes were mixed (Figure 4.8). Interestly, almost half of respondents (49%) viewed the change in external partnerships as slightly or very positive. Twenty per cent were indifferent to the change and thirty-one percent of respondents viewed them as slightly or very negative.


 
##### Part 3 - Grant Aaplication History



  


*Research Grants* 
[STILL TO COME]

The majority of respondents believe that it is now either mandatory or very important to suggest practical applications of their research in order for their grant applications to be successful. This has shifted over time, with researchers reporting that between 2006 and 2010 it was only somewhat important to do so (Figure X).

Similarly...... including partners from for-profit or non-governmental sectors in grants to be successful (Figure X).































*Perspectives on the State of Fundamental Research in Canada*
Over half of Canadian researchers who responded said that fundamental research is either very important or somewhat important to our government. Differences by career stage, discipline,ggender....

At the same time, almost three-quarters of respondents said that applied research became a higher priority for our government over the past decade. 

Summarize finding on how they think availabiltiy of research funding will change over the next five years: 




```{r, echo=FALSE, fig.cap="Reason for change in research over past 10 years. Researchers were asked if their funding proportions had changed in the past ten years (a), and what the main reason for a change in their research category (b).", fig.width=14}
## order bars from highest to lowest

# Change in the past 10 years? (yes, no, can't comment)
yes.no<-subset(research.change, select=c("Location","Country",'Country_work', "gender", "changed_10yrs"))
canada<-yes.no[yes.no$Country_work=="Canada" | (!(yes.no$Country_work=="Canada") & yes.no$Country_work=="" & yes.no$Country=="Canada"),]
canada.yesno<-data.frame(table(canada$changed_10yrs))
canada.yesno<-canada.yesno[!canada.yesno$Var1=="",]
canada.yesno$Var1<-revalue(canada.yesno$Var1, c("Can't comment (new researcher)"="Can't comment"))

canada.yesno$Var1<-factor(canada.yesno$Var1, levels=c("Yes", "No", "Can't comment"))

myColors<-(brewer.pal(9, "Blues"))
myColors<-myColors[c(9, 7,5)]
colScale <- scale_fill_manual(name = "Var1",values = myColors)

g1<-ggplot(data=canada.yesno, aes(x=Var1, y=Freq, fill=Var1))+ 
    geom_bar(stat='identity') + 
    guides(fill=FALSE) + 
    labs(x="", y="No. of responses",title="")+
   annotate('text', 3.25,635, label="(a)", size=7)+
  geom_text(aes(label=Freq), vjust=-0.5)+
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) + colScale


## GRAPH PART 2
# What is your main reason for change?
reason<-subset(research.change, select=c("Location","Country","Country_work",  "gender", "Main_reason_change_interest_related", 
                                         "Main_reason_change_Career_related", "Main_reason_change_Funding_related","Main_reason_change_Socially_related",
                                         "Main_reason_change_Other"))

canada<-reason[reason$Country_work=="Canada" | (!(reason$Country_work=="Canada") & reason$Country_work=="" & reason$Country=="Canada"),]
## switch to long format
canada.long<-gather(canada, reason.change.ca, yes.ca, -Location, -gender, -Country,-Country_work)

## using table to count cases of each category
sum.canada<-data.frame(table(canada.long$reason.change.ca, canada.long$yes.ca))
sum.canada$Var1<-revalue(sum.canada$Var1, c("Main_reason_change_Career_related" = "Career", "Main_reason_change_Funding_related" = "Funding", "Main_reason_change_interest_related" = "Interest", "Main_reason_change_Other" = "Other", "Main_reason_change_Socially_related"  = "Social"))
sum.canada$Var1<-reorder(sum.canada$Var1, -sum.canada$Freq)

myColors<-(brewer.pal(9, "Blues"))
myColors<-myColors[c(9, 8,7,6,5)]
colScale <- scale_fill_manual(name = "Var1",values = myColors)



g2<-ggplot(sum.canada, aes(x=Var1, y=Freq, fill=Var1)) + 
    geom_bar(stat='identity')+  guides(fill=FALSE) +
    theme(axis.text.x = element_text(angle=0, vjust=0.5),
          legend.position=c(0.8, 0.8), 
          legend.title=element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank()) + 
   annotate('text', 5,415, label="(b)", size=7)+ ylim(c(0, 415))+
  geom_text(aes(label=Freq), vjust=-0.5)+
  labs(x="", y="", title="")+
  colScale

grid.arrange(g1, g2, nrow=1)
```

```{r, echo=FALSE, fig.cap="Opinion of change in research over past 10 years. Researchers were asked how they viewed the change in research type."}

#canada<-subset(part1.view, Country=="Canada")
canada<-part1.view[part1.view$Country_work=="Canada" | (!(part1.view$Country_work=="Canada") & part1.view$Country_work=="" & part1.view$Country=="Canada"),]
canada<-canada[!canada$view_change_of_type=="",]

change.view.ca<-data.frame(table(canada$view_change_of_type))
change.view.ca<-change.view.ca[!change.view.ca$Var1=="",]
change.view.ca$Var1<-droplevels(change.view.ca$Var1)
# change order of the levels
change.view.ca$Var1<-factor(change.view.ca$Var1, 
                                        levels(change.view.ca$Var1)[c(5,3,1,2,4)])


myColors<-(brewer.pal(9, "Blues"))
myColors<-rev(myColors[c(7,7,7,7,7)])
colScale <- scale_fill_manual(name = "Var1",values = myColors)



ggplot(change.view.ca, aes(x=Var1, y=Freq, fill=Var1)) + geom_bar(stat='identity')+
  geom_text(aes(label=Freq, vjust=-0.5))+
  guides(fill=FALSE)+
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(angle=0, vjust=0.5)) + 
  labs(x="", y="No. of Responses") + colScale


```



